%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
\definecolor{awesome}{HTML}{414141}
%% Colors for text
\definecolor{darktext}{HTML}{414141}
\definecolor{text}{HTML}{414141}
\definecolor{graytext}{HTML}{414141}
\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
% \headersocialsep[\quad\textbar\quad]
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Miguel} \headerlastnamestyle{Cuan} \\
	\vspace{2mm}
	{\headersocialstyle{
		\faEnvelope\ mihcuan@gmail.com |
		\faPhone\ (313) 213-2955 |
		\faMapMarker\ Dearborn, MI \\
		\vspace{1mm}
		\faLinkedinSquare\ linkedin.com/in/mcuan |
		\faGithub\ github.com/mcuan}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\cvsection{Education}
\begin{cventries}
	\cventry
	{BS in Mechatronics Engineering}
	{Tecnologico de Monterrey}
	{Monterrey, Mexico}
	{Aug 2011 – Jun 2017}
	{}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-7mm}
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Connected Vehicle Embedded Software Engineer}
	{Ford Motor Company}
	{Dearborn, MI}
	{Sep 2018 – Present}
	{\begin{cvitems}
		\item {Lead developer at the Enterprise Connectivity Advanced Engineering team, supporting all stages of product development lifecycle including design, implementation, testing, validation and software integration.}
		\item {Developed C/C++ multi-threaded applications for different embedded platforms and operating systems (QNX, Embedded Linux, Android)}
		\item {Collaborated on multiple prototypes and proof-of-concepts to test new technologies for the next generation of connected vehicles.}
		\item {Coordinated software deliveries with internal and third-party suppliers for highly distributed AV systems.}
		\end{cvitems}}
	\cventry
	{Graphical User Interface Software Engineer}
	{Visteon Corporation}
	{Queretaro, Mexico}
	{Mar 2018 – Sep 2018}
	{\begin{cvitems}
		\item {Embedded software development for digital display Instrument Panel Clusters. (Ford F-150 MY21)}
		\item {C/C++ embedded software development, cross-compiled for an ARM target running QNX RTOS.}
		\item {GUI development using graphics engine to manage assets, graphics layout and rendering.}
		\item {Performed software design (UML), static and dynamic testing in compliance with coding standards (MISRA)}
		\item {Source Control / Change and Configuration Management (Git, Plastic SCM, IBM RTC, Jira) }
		\end{cvitems}}
	\cventry
	{Embedded Software Engineer}
	{Aptiv}
	{Queretaro, Mexico}
	{Jul 2017 – Mar 2018}
	{\begin{cvitems}
		\item {Embedded software development for In-Vehicle Infotainment systems. (UConnect MY19)}
		\item {Developed C++/QML embedded software applications for multiple size/resolution touchscreen displays.
			\\ (e.g. Radio AM/FM/SXM, Media, Phone [AndroidAuto, CarPlay] Navigation, Settings, HTML5 Browser)}
		\item {Developed interfaces to interact with different ECUs on the vehicle through CAN protocol.}
		\item {Performed root cause analysis to debug and fix software defects (5 Why’s, FTA, DFMEA)}
		\item {Collaborated with Systems, Integration and Validation engineers to ensure ASPICE compliance. (Peer Review, Unit Test,
		SW Integration)}
		\end{cvitems}}
	\cventry
	{Mechatronics Intern}
	{Schneider Electric}
	{Monterrey, Mexico}
	{Aug 2014 – Dec 2016}
	{\begin{cvitems}
		\item {R\&D for Miniature Circuit Breakers and other low voltage electrical protection devices (Square D, Multi-9)}
		\item {Worked with CAD software and modeling techniques for prototyping and structural simulations of miniature circuit
		breakers parts.}
		\item {Designed software for microcontroller systems and graphic user interfaces.}
		\item {Performed mechanical and electrical testing at the Power Laboratory. (UL, IEC, NEMA)}
		\item {Research collaboration having worldwide interaction with different design centers and universities.}
		\end{cvitems}}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-5mm}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming Languages:  & {\skill{\quad C/C++, Python, Java}} \\
		Software:  & {\skill{\quad Linux, QNX, Android, Git, Qt, OpenCV, ROS}} \\
		Hardware:  & {\skill{\quad x86, ARM Cortex-A, Raspberry Pi, Arduino, NVIDIA Jetson}} \\
		Other:  & {\skill{\quad CAN, Ethernet, WiFi, BLE, UWB, MQTT, Protobuf}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10mm}
\cvsection{Projects}
\vspace{-2mm}

\entrytitlestyle{Autonomous Navigation of Land Vehicles} \\
\descriptionstyle{\quad\bullet\enskip Implemented algorithms in C++ to process LiDAR point cloud data and identify traversable space, obstacles and routes, performing real time} \\
\descriptionstyle{\quad\quad data processing and wireless data transmission.} \\
\descriptionstyle{\quad\bullet\enskip Utilized ROS to integrate the robotic platform solution and generate a visual 3D map of the environment.}


\entrytitlestyle{Residential Energy Management System} \\
\descriptionstyle{\quad\bullet\enskip Contributed to the development of energy monitoring systems for residential electrical installations, leading to company award and patent.} \\
\descriptionstyle{\quad\bullet\enskip Designed and prototyped electromechanical systems and implemented embedded software for an IoT end-to-end energy metering solution.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-2mm}
\cvsection{Achievements}
\begin{cvhonors}
	\cvhonor
	{Silver Prize at FD Innovation Contest}
	{Impacting strongly traditional products}
	{Schneider Electric}
	{Dec 2016}
	\cvhonor
	{Patent US 9618548}
	{Integrated Systems for Miniature Circuit Breaker Load Centers}
	{Schneider Electric}
	{Apr 2017}
\end{cvhonors}

\end{document}